Yeast RNA-seq 48 sample simulation study

### 2018-07-19 datasets/RNA-Seq/yeast-simulation.Rmd
Adjust nmids and densknots for scott-empirical

```{r}
bd <- initializeBenchDesign()
bd <- addBMethod(bd, "scott-theoretical",
                     FDRreg::FDRreg,
                     function(x) { x$FDR },
                     z = test_statistic,
                     features = model.matrix( ~  splines::bs(ind_covariate, df = 3) - 1),
                     nulltype = 'theoretical',
                     control = list(lambda = 0.01))
bd <- addBMethod(bd, "scott-empirical",
                     FDRreg::FDRreg,
                     function(x) { x$FDR },
                     z = test_statistic,
                     features = model.matrix( ~  splines::bs(ind_covariate, df = 3) - 1),
                     nulltype = 'empirical',
                     control = list(lambda = 0.01))
```

@@

```{r}
#' @param X simnumber
#' @param seed random seed
#' @param dds is the full DESeq2 dataset
#' @param resFULL is the results object from running DESeq2 on dds (used in
#'   to obtain the fold change effect sizes when adding non-null genes)
#' @param sampleSize is the number of samples in each condition
#' @param nDE is the number of DE genes
#' @param bd is the bench design object
#' @param BPPARAM is the BiocParallel bpparam argument to pass to DESeq. Since
#'  parallelization happens by forking multiple instances of this function, we 
#'  will specify only one worker per DEseq intance.
#' @param uninformativeCovariate logical indicating whether to replace overall mean 
#'  independent covariate with a randomly generated (uninformative) covariate. 
#'  Default is FALSE.
#' @param pvalHists logical whether to return histograms of pvalues by covariate
#'  instead of SB objects
simulateOneSplit <- function(X, rseed, dds, resFULL, nDE, sampleSize,
                             bd, uninformativeCovariate = FALSE, pvalHists = FALSE){

@@

  geneExp <- tbl_df(data.frame(geneName=rownames(resTEST), 
                               pval=resTEST$pvalue, 
                               SE=resTEST$lfcSE,                 
                               ind_covariate = resTEST$baseMean,
                               effect_size = resTEST$log2FoldChange, 
                               test_statistic = resTEST$stat,
                               qvalue = truth,
                               pzero = rowSums(counts(dds_test)==0)/
                                       ncol(counts(dds_test)))) %>%
                dplyr::filter(!is.na(pval))

  if(uninformativeCovariate)
    geneExp$ind_covariate <- rnorm(nrow(geneExp))

>>>>

```{r}
bd <- initializeBenchDesign()
bd <- addBMethod(bd, "scott-theoretical",
                     FDRreg::FDRreg,
                     function(x) { x$FDR },
                     z = test_statistic,
                     features = model.matrix( ~  splines::bs(ind_covariate, df = 3) - 1),
                     nulltype = 'theoretical',
                     control = list(lambda = 0.01))
bd <- addBMethod(bd, "scott-empirical",
                     FDRreg::FDRreg,
                     function(x) { x$FDR },
                     z = test_statistic,
                     features = model.matrix( ~  splines::bs(ind_covariate, df = 3) - 1),
                     nulltype = 'empirical',
                     control = list(lambda = 0.01, nmids = 300, densknots = 20))
```

@@

```{r}
#' @param X simnumber
#' @param seed random seed
#' @param dds is the full DESeq2 dataset
#' @param resFULL is the results object from running DESeq2 on dds (used in
#'   to obtain the fold change effect sizes when adding non-null genes)
#' @param sampleSize is the number of samples in each condition
#' @param nDE is the number of DE genes
#' @param bd is the bench design object
#' @param BPPARAM is the BiocParallel bpparam argument to pass to DESeq. Since
#'  parallelization happens by forking multiple instances of this function, we 
#'  will specify only one worker per DEseq intance.
#' @param uninformativeCovariate logical indicating whether to replace overall mean 
#'  independent covariate with a randomly generated (uninformative) covariate. 
#'  Default is FALSE.
#' @param pvalHists logical whether to return histograms of pvalues by covariate
#'  instead of SB objects
simulateOneSplit <- function(X, rseed, dds, resFULL, nDE, sampleSize,
                             bd, uninformativeCovariate = FALSE, pvalHists = FALSE){
  if(uninformativeCovariate)
    uninf_covar <- rnorm(nrow(dds))

@@

  geneExp <- tbl_df(data.frame(geneName=rownames(resTEST), 
                               pval=resTEST$pvalue, 
                               SE=resTEST$lfcSE,                 
                               ind_covariate = resTEST$baseMean,
                               effect_size = resTEST$log2FoldChange, 
                               test_statistic = resTEST$stat,
                               qvalue = truth,
                               pzero = rowSums(counts(dds_test)==0)/
                                       ncol(counts(dds_test))))

  if (uninformativeCovariate)
    geneExp <- mutate(geneExp, ind_covariate = uninf_covar)

  geneExp <-  geneExp %>% dplyr::filter(!is.na(pval)) %>% dplyr::filter(pzero < 0.5)
